Meta-analysis on sex in MSSM-Penn-Pitt and HBCC ACC/DLPFC

### 2020-08-01 individual-cohorts/meta-analysis.Rmd
save meta-analysis output to Synapse

```{r input_data}
mpp_acc <- readr::read_tsv(synGet("syn22278494")$path) %>% 
  dplyr::select(Comparison, gene_id, AveExpr, t, logFC, P.Value, adj.P.Val)
mpp_dlpfc <- readr::read_tsv(synGet("syn22278597")$path) %>% 
  dplyr::select(Comparison, gene_id, AveExpr, t, logFC, P.Value, adj.P.Val)
hbcc_dsACC <- readr::read_tsv(synGet("syn22280959")$path) %>% 
  dplyr::select(Comparison, gene_id, AveExpr, t, logFC, P.Value, adj.P.Val) 
hbcc_dlpfc <- readr::read_tsv(synGet("syn22280588")$path) %>% 
  dplyr::select(Comparison, gene_id, AveExpr, t, logFC, P.Value, adj.P.Val)
```

@@

>>>>

```{r input_data}
mpp_acc <- readr::read_tsv(synGet("syn22278494")$path) %>% 
  dplyr::select(Comparison, gene_id, AveExpr, t, logFC, P.Value, adj.P.Val)
mpp_dlpfc <- readr::read_tsv(synGet("syn22278597")$path) %>% 
  dplyr::select(Comparison, gene_id, AveExpr, t, logFC, P.Value, adj.P.Val)
hbcc_dsACC <- readr::read_tsv(synGet("syn22280959")$path) %>% 
  dplyr::select(Comparison, gene_id, AveExpr, t, logFC, P.Value, adj.P.Val) 
hbcc_dlpfc <- readr::read_tsv(synGet("syn22280588")$path) %>% 
  dplyr::select(Comparison, gene_id, AveExpr, t, logFC, P.Value, adj.P.Val)
Ids <- c("syn22278494", "syn22278597", "syn22280959", "syn22280588")
```

@@

```{r store}
# Code
CODE <- Folder(name = "Meta-analysis on sex", parentId = parentId)
CODE <- synStore(CODE)

# Store meta-analysis
res_dlpfc %>%
  write.table(file = 'CMC_dlpfc_Sex_meta_analysis.tsv', sep = '\t', row.names=F, quote=F)
nEXP_OBJ = File('CMC_dlpfc_Sex_meta_analysis.tsv', 
                name = 'Sex Normalised, meta-analysis (DLPFC)', 
                parentId = CODE$properties$id)
nEXP_OBJ = synStore(nEXP_OBJ, used = Ids, activityName = activityName, 
                    executed = thisFile, activityDescription = activityDescription)
res_acc %>%
  write.table(file = 'CMC_acc_Sex_meta_analysis.tsv', sep = '\t', row.names=F, quote=F)
nEXP_OBJ = File('CMC_acc_Sex_meta_analysis.tsv', 
                name = 'Sex Normalised, meta-analysis (ACC)', 
                parentId = CODE$properties$id)
nEXP_OBJ = synStore(nEXP_OBJ, used = Ids, activityName = activityName, 
                    executed = thisFile, activityDescription = activityDescription)
```
